\section{Lesson 1}
\subsection{Content}
\begin{enumerate}
\item Column vectors can hold complex numbers.
\end{enumerate}
\subsection{Memory Items}
\begin{enumerate}
    \item A \textbf{\emph{scalar}} is a number, typically either real or complex, by which vector may be multiplied.
    \item A \textbf{\emph{linear combination}} of a set of vectors $\{ {\textbf x}_1,\dots,{\textbf x}_k \}$ is any vector that can be expressed as $\alpha_1{\textbf x}_1+\cdots+\alpha_k{\textbf x}_k$ where $\alpha_1,\dots,\alpha_k$ are scalars.
    \item When ${\textbf x}=\alpha_1{\textbf x}_1+\cdots+\alpha_k{\textbf x}_k$ the scalars are said to be the \textbf{coordinates}, \textbf{expansion coefficients}, or simply \textbf{coefficients} of ${\textbf x}$ with respect to $\{{\textbf x}_1,\dots,{\textbf x}_k\}$.
    \item A linear combination is an \textbf{affine combination} if and only if the sum of its coefficients is 1.
    \item A set of vectors is \textbf{affine} if and only if it is closed under affine combination.
    \item A nonempty affine set of vectors in $\mathbb{R}^{3}$ is a point, a line, a plane or a space.  (geometric observation)
    \item The dot product of two vectors ${\textbf x}$ and ${\textbf y}$, ${\textbf x}\cdot{\textbf y}=x_1y_1+\cdots+x_n y_n$, equal the product of the lengths of the vectors, $||{\textbf x}||$ and $||{\textbf y}||$, with the cosine of the angle between them. (geometric observation) (${\textbf x}\cdot{\textbf y}=||{\textbf x}|| ||{\textbf y}|| \cos{\theta}$)
    \item Cauchy-Scwarz: $|{\textbf x}\cdot{\textbf y}|\le || {\textbf x}||\, ||{\textbf y}||$ 
    \item Two vectors are \textbf{orthogonal} if and only if their dot product is zero.
    \item Perpendicular vectors are orthogonal. (geometrix observation)
    \item The zero vector is orthogonal to all vectors having the same number of components, but perpendicular to none of them.
\end{enumerate}